---
title: "Research Help Desk Statistics Report"
params:
  fpath: "C:/Users/briney/Documents/JobDocs/LibStats/Reports/data"
  periodStart: "2018-01-22 00:00:00"
  periodEnd: "2018-05-20 23:59:59"
output:
  pdf_document: 
    fig_width: 7
    fig_height: 3
---

<!--
## Name: LibStats_report_RHD.Rmd
## Created: June 2018 by Kristin Briney
## Purpose: This Rmarkdown template will create a report for the Research Help Desk
##          using cleaned StatBot data. Date ranges must be specified.
-->

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning=FALSE, message=FALSE)
library(tidyverse)
library(stringr)
library(lubridate)
library(knitr)

  depart <- params$dept
  pStart <-  ymd_hms(params$periodStart)
  pEnd <-  ymd_hms(params$periodEnd)


  ## Load transaction data
  
  finput <- paste(params$fpath, "Trans.csv", sep="/")
  Trans_all <- read_csv(finput)
  
  Trans <- filter(Trans_all, Trans_all$Location=="Research Help Desk" &
                    Trans_all$TransDateTime>=pStart & 
                    Trans_all$TransDateTime<=pEnd)
  Trans <- add_column(Trans, Week=week(Trans$TransDateTime))
  Trans <- add_column(Trans, WeekDay=wday(Trans$TransDateTime))
  Trans <- add_column(Trans, Hour=hour(Trans$TransDateTime))
```

### Research Help Desk

### Time period: `r pStart` to `r pEnd`



## Transactions

__Total Research Help Desk transactions = `r count(Trans)`__

### Staff Transactions

```{r Tparams}
  TstaffName <- group_by(Trans, StaffName) %>% mutate(total=n()) %>% 
    select(StaffName, total) %>% unique() %>% arrange(desc(total), StaffName)
  
  kable(TstaffName, format="latex")

```

### Transaction Patron Status

```{r TuserType}
  TuserTypes <- group_by(Trans, UserStatus) %>% mutate(total=n()) %>% 
    select(UserStatus, total) %>% unique() %>% arrange(desc(total))
  
  ggplot(data=TuserTypes, mapping=aes(x=UserStatus, y=total, label=total)) +
    theme_light() + 
    theme(legend.position="none") +
    geom_col(fill="#999999") +
    geom_text() +
    labs(x="User Status", y="Number of Transactions")
```

### Transaction Course Departments

_Departments listed if they had 2 or more transactions_

```{r TuserDept}
  TuserDept <- group_by(Trans, Department) %>% mutate(total=n()) %>% 
    select(Department, total) %>% unique() %>% 
    filter(total > 1  & Department != "NA") %>% arrange(desc(total), Department)

  kable(TuserDept, format="latex")
  
```

### Transaction Type

_Transactions can be coded as multiple types, meaning the sum of the totals
in each category may excede the total number of transactions_

```{r Ttype}
  Ttype_type <- bind_rows(tibble(Ttype="Directional"), tibble(Ttype="Informational"),
                              tibble(Ttype="Referral"), tibble(Ttype="Reference"))
  Ttype_total <- bind_rows(count(filter(Trans,Directional==TRUE)), 
                               count(filter(Trans, Informational==TRUE)),
                               count(filter(Trans, Referral==TRUE)),
                               count(filter(Trans, Reference==TRUE)))
  Ttype <- bind_cols(Ttype_type, Ttype_total)
  
  ggplot(data=Ttype, mapping=aes(x=Ttype, y=n, label=n)) +
    theme_light() + 
    theme(legend.position="none") +
    geom_col(fill="#999999") +
    geom_text() +
    labs(x="Type", y="Number of Transactions")
```

### Transaction Format

```{r Tform}
  Tform <- group_by(Trans, Format) %>% mutate(total=n()) %>% 
    select(Format, total) %>% unique() %>% 
    filter(Format=="in person/face to face" | Format=="on the phone" | Format=="over e-mail") %>% 
    arrange(desc(total))

  ggplot(data=Tform, mapping=aes(x=Format, y=total, label=total)) +
    theme_light() + 
    theme(legend.position="none") +
    geom_col(fill="#999999") +
    geom_text() +
    labs(x="Format", y="Number of Transactions")
```

### Transactions by Week of the Year

```{r TweekNum}
  TweekNum <- group_by(Trans, Week) %>% mutate(total=n()) %>% 
    select(Week, total) %>% unique() %>% arrange(Week)


  ggplot(data=TweekNum, mapping=aes(x=Week, y=total, label=total)) +
    theme_light() + 
    theme(legend.position="none") +
    geom_col(fill="#999999") +
    geom_text() +
    labs(x="Week of the Year", y="Number of Transactions")
```

### Transactions by Weekday and Hour

_1 = Sunday_

```{r TweekDayHour}
  TweekDayHour <- group_by(Trans, WeekDay, Hour) %>% mutate(total=n()) %>% 
    select(WeekDay, Hour, total) %>% unique() %>% arrange(WeekDay, Hour)

  #kable(TweekDayHour, format="html")

  ggplot(data=TweekDayHour, mapping=aes(x=Hour, y=total)) +
    theme_light() + 
    theme(legend.position="none") +
    geom_col(fill="#999999") +
    facet_wrap(~ WeekDay, nrow=1) +
    labs(x="Hour", y="Number of Transactions")
```
